---
output:
  github_document
---

# README

This repository contains an R package, `LDcompute` to compute LD using SNPRelate functions and return results in a consistent format.
It also includes an example wrapper script (`compute_ld.R`) and test data (`testdata/`) to show how it can be used.

## Calling functions directly

Load other packages.
```{r}
library(SeqArray)
```

Load the `LDcompute` package.

```
library(LDcompute)
```
```{r, echo = FALSE, include = TRUE}
devtools::load_all("LDcompute")
```

Open the gds file:

```{r}
gds <- seqOpen("testdata/1KG_phase3_subset.gds")
```

Choose the sample set:
```{r}
sample_include <- seqGetData(gds, "sample.id")[1:500]
```

### LD between a pair of variants

```{r}
compute_ld_pair(gds, 1, 2, sample_include = sample_include)
```

Using other methods:
```{r}
compute_ld_pair(gds, 1, 2, sample_include = sample_include, ld_methods = c("r2", "dprime"))
```

### LD between an index variant and a set of other variants

```{r}
compute_ld_index(gds, 1, c(2:10), sample_include = sample_include)
```

Using other methods:
```{r}
compute_ld_index(gds, 1, c(2:10), sample_include = sample_include, ld_methods = c("r2", "dprime"))
```

### LD between all pairs in a set of variants


```{r}
compute_ld_set(gds, c(1:4), sample_include = sample_include)
```

Using other methods:
```{r}
compute_ld_set(gds, c(1:4), sample_include = sample_include, ld_methods = c("r2", "dprime"))
```

## Cleanup

```{r}
seqClose(gds)
```

## Running compute_ld.R with test data

### LD between a pair of variants

```
R --no-save --args \
  testdata/1KG_phase3_subset.gds \
  --ld_methods r2 dprime \
  --variant_include_file_1 testdata/variant_include_pair_1.rds \
  --variant_include_file_2 testdata/variant_include_pair_2.rds \
  --sample_include_file testdata/sample_include.rds \
  --out_prefix pair \
  < compute_ld.R
```

This creates a file called `pair_ld.rds`.

### LD between an index variant and a set of other variants

```
R --no-save --args \
  testdata/1KG_phase3_subset.gds \
  --ld_methods r2 dprime \
  --variant_include_file_1 testdata/variant_include_index_1.rds \
  --variant_include_file_2 testdata/variant_include_index_2.rds \
  --sample_include_file testdata/sample_include.rds \
  --out_prefix index \
  < compute_ld.R
```

This creates a file called `index_ld.rds`.

### LD between all pairs in a set of variants

```
R --no-save --args \
  testdata/1KG_phase3_subset.gds \
  --ld_methods r2 dprime \
  --variant_include_file_1 testdata/variant_include_set_1.rds \
  --sample_include_file testdata/sample_include.rds \
  --out_prefix set \
  < compute_ld.R
```

This creates a file called `set_ld.rds`.
